Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-03-23 main.tex
:pencil: Low-complexity algorithm

			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee. In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD). In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Huang2010}. Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution. Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}. The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
						\State Set $q^{\star}=\arg\max_q{\tilde{z}(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

		\begin{subsection}{Waveform and Splitting Ratio}
			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}}$. On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$. Hence, rate \eqref{eq:R} and DC current \eqref{eq:z_expand} reduce respectively to \eqref{eq:R_waveform} and \eqref{eq:z_waveform}, and problem~\eqref{op:original} boils down to
			\begin{figure*}[!b]
				\hrule
				\begin{align}
					R(\boldsymbol{s}_{\mathrm{I}},\rho)
					& = \log_2\left(\prod_{n=1}^N\biggl(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\biggr)\right),\label{eq:R_waveform}\\
					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).&&\label{eq:z_waveform}
				\end{align}
			\end{figure*}%
			\begin{maxi!}
				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}.}
			\end{maxi!}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity w.r.t. the number of subbands \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two low-complexity waveform amplitude design by combining WF and SMF under TS and PS setups. The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005} and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. $\alpha = 1$ corresponds to a standard matched filter where the amplitude of sinewave $n$ is linearly proportional to the equivalent channel strength $\lVert{\boldsymbol{h}_n}\rVert$, while $\alpha > 1$ further elevates the strong subbands and suppresses the weak ones.

			In the low-complexity TS waveform design, modulated waveform is used in the data session while multisine waveform is used in the energy session, and their amplitudes are given respectively by \eqref{eq:wf} and \eqref{eq:smf}. The R-E boundary is a segment between the WIT point ($\eta=0$) and the WPT point ($\eta=1$).

			% For the WIT point, we

			On the other hand, the low-complexity PS scheme controls the superposed waveform by balancing ratio $\delta$ and involves the design of splitting ratio $\rho$. The amplitude of modulated and multisine components are
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{align}

			Note that the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform while the splitting ratio $\rho$ denotes the proportion used for energy harvesting. For low-complexity PS design, we characterize the achievable R-E region by varying $\delta$ and $\rho$ from \num{0} to \num{1} such that the rate constraint \eqref{co:irs_rate} in the passive beamforming problem can be dropped (i.e. set $\bar{R}=0$).

			Moreover, the low-complexity TS design can be regarded as a special case where

			The low-complexity algorithm for joint waveform, active and passive beamforming design under TS and PS modes is summarized in Algorithm~.

			% In contrast, the R-E boundary of low-complexity TS design is a segment

			\begin{algorithm}[!t]
				\caption{Low-Complexity Design under TS and PS Modes.}
				\label{al:lc}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\delta,\rho,\sigma_n,\bar{R}=0,Q,\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P}}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$
					\State Get $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:sca}
						\State Update $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)}$ based on $\boldsymbol{h}_n^{(i)}$, $\forall n$ by \eqref{eq:wf}, {eq:smf}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $z^{(i)}$ by \eqref{eq:z_waveform}
					\Until $\lvert z^{(i)} - z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{section}

@@

>>>>

			Note that problem~\eqref{op:irs} is not a Semidefinite Programming (SDP) such that relaxing the rank constraint \eqref{co:irs_rank} has no analytical performance guarantee. In Section~\ref{se:performance_evaluation}, we prove through numerical simulations that the solution $\boldsymbol{\Phi}^{\star}$ to \ref{ob:irs} -- \ref{co:irs_sd} is rank-\num{1} under different configurations for all tested channel realizations. It suggests that the rank constraint \eqref{co:irs_rank} can be dropped with negligible loss and $\bar{\boldsymbol{\phi}}^\star$ can be directly obtained through Eigenvalue Decomposition (EVD). In case $\boldsymbol{\Phi}^{\star}$ is not rank-\num{1}, a suboptimal solution can be extracted via the Gaussian randomization method \cite{Huang2010}. Specifically, we decompose $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$, generate CSCG random vector $q \in \{1, \dots, Q\}$ by $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, construct the candidate $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)}$, and choose the $\bar{\boldsymbol{\phi}}^\star$ that maximizes \eqref{ob:irs} as the solution. Finally, the phase shift of element $l$ is retrieved by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2013}. The SCA algorithm of passive beamforming is summarized in Algorithm~\ref{al:sca}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,\bar{R},Q,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Get $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
					\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
						\State Set $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)},\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

		\begin{subsection}{Waveform and Splitting Ratio}
			Next, we jointly optimize the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and the splitting ratio $\rho$ for any given IRS phase shift $\boldsymbol{\phi}$ and active precoder $\boldsymbol{b}_{\mathrm{I/P}}$. On top of \eqref{eq:b}, the equivalent channel strength at subband $n$ is $\lVert{\boldsymbol{h}_n}\rVert$ and the power allocated to the modulated/multisine waveform is $s_{\mathrm{I/P},n}^2$. Hence, rate \eqref{eq:R} reduces to
			\begin{equation}\label{eq:R_waveform}
				R(\boldsymbol{s}_{\mathrm{I}},\rho) = \log_2\prod_{n=1}^N\left(1+\frac{(1-\rho)\lVert{\boldsymbol{h}_n}\rVert^2 s_{\mathrm{I},n}^2}{\sigma_n^2}\right)
			\end{equation}
			and DC current \eqref{eq:z_expand} reduces to \eqref{eq:z_waveform}, so that problem~\eqref{op:original} boils down to
			\begin{figure*}[!b]
				\hrule
				\begin{align}
					z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)
					& = \frac{1}{2}{\beta_2}{\rho} \sum_{n=1}^N \lVert{\boldsymbol{h}_n}\rVert^2(s_{\mathrm{I},n}^2+s_{\mathrm{P},n}^2) + \frac{3}{8}{\beta_4}{\rho^2} \left( 2\sum_{n_1,n_2} \prod_{j=1}^2 \lVert{\boldsymbol{h}_{n_j}}\rVert^2 s_{\mathrm{I},{n_j}}^2 + \sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}} \prod_{j=1}^4 \lVert{\boldsymbol{h}_{n_j}}\rVert s_{\mathrm{P},{n_j}} \right)\nonumber\\
					& \quad + \frac{3}{2}{\beta_4}{\rho^2} \left( \sum_{n_1,n_2} \lVert{\boldsymbol{h}_{n_1}}\rVert^2 \lVert{\boldsymbol{h}_{n_2}}\rVert^2 s_{\mathrm{I},{n_1}}^2 s_{\mathrm{P},{n_2}}^2 \right).&&\label{eq:z_waveform}
				\end{align}
			\end{figure*}
			\begin{maxi!}
				{\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho}{z(\boldsymbol{s}_{\mathrm{I}},\boldsymbol{s}_\mathrm{P},\rho)}{\label{op:waveform}}{}
				\addConstraint{\frac{1}{2}\left(\lVert{\boldsymbol{s}_{\mathrm{I}}}\rVert^2+\lVert{\boldsymbol{s}_\mathrm{P}}\rVert^2\right)\le{P}}
				\addConstraint{R(\boldsymbol{s}_{\mathrm{I}},\rho) \ge \bar{R}.}
			\end{maxi!}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality at a cost of exponential computational complexity \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two low-complexity waveform amplitude design by combining WF and SMF under TS and PS setups. The optimal waveform design for WIT corresponds to the WF strategy that assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\mu$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005} and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ scales the matched filter to exploit the rectifier nonlinearity. In the low-complexity TS waveform design, modulated waveform \eqref{eq:wf} is used in the data session while multisine waveform \eqref{eq:smf} is used in the energy session. In contrast, the low-complexity PS scheme jointly designs the waveform balancing ratio $\delta$ and splitting ratio $\rho$, and the amplitude of modulated and multisine components are given by
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\mu - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+} \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha \label{eq:s_p}
			\end{align}

			Besides, minor modification is required for passive beamforming to cooperate with the low-complexity waveform schemes. To achieve the WIT point ($\eta=\rho=0$), the achievable rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:z_irs_approx} should be maximized. To achievable non-WIT points, the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is now characterized by varying $\eta$, $\delta$ and $\rho$. Algorithm~\ref{al:lc} summarizes the modified passive beamforming design under low-complexity PS setup.

			\begin{algorithm}[!t]
				\caption{Modified: IRS Phase Shift.}
				\label{al:lc}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\boldsymbol{w}_{\mathrm{I/P},n},\rho,\sigma_n,Q,\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\If{$\rho=0$}
						\State Get $\boldsymbol{\Phi}^{\star}$ by maximizing \eqref{eq:R_irs} w.r.t. \eqref{co:irs_modulus}, \eqref{co:irs_sd}
					\Else
						\Repeat
							\State $i \gets i + 1$
								\State Set $\bar{R}=0$
								\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \ref{ob:irs} -- \ref{co:irs_sd}
								\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
								\State Compute $z^{(i)}$ by \eqref{eq:z_irs}
						\Until $\lvert z^{(i)}-z^{(i-1)} \rvert \le \epsilon$
						\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\EndIf
					\If{$\mathrm{rank}(\boldsymbol{\Phi}^{\star})=1$}
						\State Get $\bar{\boldsymbol{\phi}}^\star$ by EVD, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\Else
						\State Get $\boldsymbol{U},\boldsymbol{\Sigma}$ by EVD, $\boldsymbol{\Phi}^{\star}=\boldsymbol{U}\boldsymbol{\Sigma}\boldsymbol{U}^H$
						\State Generate $\boldsymbol{r}_q \sim \mathcal{CN}(\boldsymbol{0},\boldsymbol{I}_{L+1})$, $\forall q$
						\State Construct $\bar{\boldsymbol{\phi}}_q=e^{j\arg\left(\boldsymbol{U}\boldsymbol{\Sigma}^{1/2}\boldsymbol{r}_q\right)},\boldsymbol{\Phi}_q=\bar{\boldsymbol{\phi}}_q\bar{\boldsymbol{\phi}}_q^H$, $\forall q$
						\State Set $q^{\star}=\arg\max_q{R(\boldsymbol{\Phi}_q)}$ or $q^{\star}=\arg\max_q{z(\boldsymbol{\Phi}_q)}$, $\bar{\boldsymbol{\phi}}^\star=\bar{\boldsymbol{\phi}}_{q^{\star}}$
					\EndIf
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

			Similar to Algorithm~\ref{al:bcd}, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:lc}, the active beamforming $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ by \eqref{eq:wf}, \eqref{eq:smf} for TS or \eqref{eq:s_i}, \eqref{eq:s_p} for PS, until convergence.
		\end{subsection}
	\end{section}

@@

		% (denotes the proportion allocated to the multisine waveform) (denotes the proportion used for energy harvesting)
		% The R-E boundary is a segment between the WIT point and the WPT point.
		% where the balancing ratio $\delta$ denotes the proportion allocated to the multisine waveform and the splitting ratio $\rho$ denotes the proportion used for energy harvesting. The R-E region is characterized under different $\delta$ and $\rho$ from \num{0} to \num{1}.
